---
title: "Stock Markets Application"
author: "Germ치n Hern치ndez"
date: "31/7/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Summary
This is a very simple application that use yahoo to construct and show some american stock market graphs since 2017-01-03. You can choose between:

- Apple
- Cisco
- IBM
- Facebook
- Twitter
- Microsoft and
- Google

## Reproducible Pitch

This is a task for the data science coursera course about developing data products for week 4. As part of this, I have created a shiny app and deployed it on the shiny server. The link is https://germanhdzc.shinyapps.io/Stockmarket/. The code can be found at https://github.com/GermanHdzC/DDP.

## UI code

```{r cars, echo = TRUE, eval=FALSE}
library(shiny)
library(quantmod)

# Define UI for application that draws a histogram
ui <- fluidPage(
    
    # Application title
    titlePanel("Mercados con R"),
    
    # Sidebar with a slider input for number of bins 
    sidebarLayout(
        sidebarPanel("Seleccione las acciones que desee consultar",
                     selectInput("accion",
                                 label="Acci칩n",
                                 choices=c("Apple"="AAPL",                                      "Cisco"="CSCO",
                                           "Cisco"="CSCO",
                                           "IBM"="IBM",
                                           "Facebook"="FB",
                                           "Twitter"="TWTR",
                                           "Microsoft"="MSFT",
                                           "Google"="GOOG"))
        ),
        
        # Show a plot of the generated distribution
        mainPanel("Gr치fico de acciones del mercado de valores Americano",
                  plotOutput("grafico")
        )
    )
)
```

## Server code

```{r, echo=TRUE, eval=FALSE}
# Define server logic required to draw a histogram
server <- function(input, output) {
    
    output$grafico = renderPlot({
        stockdata = getSymbols(input$accion, src="yahoo",
                               auto.assign=FALSE)
        candleChart(stockdata, name=input$accion)
    })
}

```

